Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-11-17 nips_2018.tex
progress on poster

\begin{table}[t]
  \caption{Drawings (left), their specs (middle left), and programs synthesized from those specs (middle right). Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands. Note the nested loops in second figure, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
%  \vspace{-0.6cm}
\centering  \begin{tabular}{m{1.5cm}llc}
    \toprule
    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
      \textbf{Compression factor}%\\\textbf{factor}
      %      \end{tabular}\\
      \\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{lstlisting}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
for(i<3)
 line(i,-1*i+6,
      2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{lstlisting}
     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(5,13,2,10,arrow)
%% Circle(5,9)
%% Circle(8,5)
%% Line(2,8, 2,6,arrow)
%% Circle(2,5)
%% \end{lstlisting}
%% \small\emph{... etc. ...; 13 lines}
%% \end{minipage}&
%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
%% circle(4,10)
%% for(i<3)
%%  circle(-3*i+7,5)
%%  circle(-3*i+7,1)
%%  line(-3*i+7,4,-3*i+7,2,arrow)
%%  line(4,9,-3*i+7,6,arrow)
%% \end{lstlisting}
%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
%%     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Circle(5,8)
%% Circle(2,8)
%% Circle(8,11)
%% Line(2,9, 2,10)
%% Circle(8,8)
%% Line(3,8, 4,8)
%% Line(3,11, 4,11)
%% \end{lstlisting}
%%   \small\emph{... etc. ...; 21 lines}
%% \end{minipage}&\begin{minipage}{\exampleProgramSize}
%% \begin{lstlisting}
%% for(i<3)
%%  for(j<3)
%%   if(j>0)
%%    line(-3*j+8,-3*i+7,
%%         -3*j+9,-3*i+7)
%%    line(-3*i+7,-3*j+8,
%%         -3*i+7,-3*j+9)
%%   circle(-3*j+7,-3*i+7)
%% \end{lstlisting}
%% \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Rectangle(1,10,3,11)
Rectangle(1,12,3,13)
Rectangle(4,8,6,9)
Rectangle(4,10,6,11)
\end{lstlisting}
  \small\emph{... etc. ...; 16 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<4)
 for(j<4)
  rectangle(-3*i+9,-2*j+6,
            -3*i+11,-2*j+7)
\end{lstlisting}
\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(11,14,13,14,arrow)
%% Circle(10,10)
%% Line(10,13,10,11,arrow)
%% Circle(6,10)
%% \end{lstlisting}
%%     \small\emph{... etc. ...; 15 lines}
%% \end{minipage}&
%% \begin{minipage}{\exampleProgramSize}
%%     \begin{lstlisting}
%% for(i<4)
%%  line(-4*i+13,4,-4*i+13,2,arrow)
%%  for(j<3)
%%   if(j>0)
%%    circle(-4*i+13,4*j+-3)
%%   line(-4*j+10,5,-4*j+12,5,
%%        arrow)
%% \end{lstlisting}
%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule

  \includegraphics[width = \exampleDrawingSize]{figures/expert-71-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(3,10,3,14,arrow)
Rectangle(11,8,15,10)
Rectangle(11,14,15,15)
Line(13,10,13,14,arrow)
  \end{lstlisting}\small\emph{... etc. ...; 16 lines}
  \end{minipage}&\begin{minipage}{\exampleProgramSize}
%% \begin{lstlisting}
%% for (i<3)
%%  circle(-3*i+7,1)
%%  circle(-3*i+7,6)
%%  line(-3*i+7,-1*i+4,-3*i+7,5)
%% \end{lstlisting}
\begin{lstlisting}
for(i<3)
 line(7,1,5*i+2,3,arrow)
 for(j<i+1)
  if(j>0)
   line(5*j-1,9,5*i,5,arrow)
  line(5*j+2,5,5*j+2,9,arrow)
 rectangle(5*i,3,5*i+4,5)
 rectangle(5*i,9,5*i+4,10)
rectangle(2,0,12,1)
\end{lstlisting}
\end{minipage}&$\frac{16}{9} = 1.8\text{x}$\\\midrule

@@

\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Circle(2,8)
Rectangle(6,9, 7,10)
Circle(8,8)
Rectangle(6,12, 7,13)
Rectangle(3,9, 4,10)
\end{lstlisting}\small\emph{... etc. ...; 9 lines}
  \end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
reflect(y=8)
 for(i<3)
  if(i>0)
   rectangle(3*i-1,2,3*i,3)
  circle(3*i+1,3*i+1)
\end{lstlisting}
\end{minipage}&$\frac{9}{5} = 1.8\text{x}$ \\\bottomrule
  \end{tabular}
  \end{table}

@@

Given a search policy, what is the best way of using it to quickly find minimum cost programs?
We use a bias-optimal search algorithm (c.f. Schmidhuber 2004~\citep{schmidhuber2004optimal}):

\noindent\textbf{Definition: Bias-optimality.} 
   A search algorithm is $n$-\emph{bias optimal}
with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
guaranteed to find a solution in $\sigma $ after searching for at least time
$n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
takes to verify that $\sigma $ contains a solution to the
search problem.

%Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
Bias-optimal search over program spaces is known as \textbf{Levin
  Search}~\cite{levin1973universal}; an example of a $1$-bias optimal
search algorithm is an ideal time-sharing system that allocates
$\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
We construct a $1$-bias optimal search algorithm by identifying
$\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and
$t(\sigma ) = t(\sigma|S)$, where $t(\sigma|S)$ is how long the
synthesizer takes to search $\sigma $ for a program for
$S$. Intuitively, this means that the search algorithm explores the
entire program space, but spends most of its time in the regions of
the space that the policy judges to be most promising.  Concretely,
this means that our synthesis strategy is to run many different
program searches \emph{in parallel} (i.e., run in parallel different
instances of the synthesizer, one for each $\sigma$), but to
allocate compute time to a $\sigma $ in proportion to
$\pi_\theta(\sigma |S)$.

%% \begin{figure}\centering
%%   \begin{tikzpicture}
%%     \node[anchor = west] at (0,5.25) {Entire program search space};
%%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
%%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
%%     \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
%%     \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
%%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
%%     \draw (0,2) -- node[above,sloped]{long programs} (4,0);
%%     \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
%%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
%%     \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
%%     \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
%%     \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
%%     \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
%%     \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
%%     \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
%%     \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
%%     \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
%%     \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
%%   \end{tikzpicture}
%%   \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs. For example, one subspace might be short programs which don't loop. The policy $\pi$ predicts a distribution over program subspaces. The weight that $\pi$ assigns to a subspace is indicated by it's yellow shading in the above figure.}
%%   \end{figure}
Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
But the actual runtime of the algorithm depends strongly upon
the bias $\probability_{\text{bias}}[\cdot ]$.
Our new approach is to learn $\probability_{\text{bias}}[\cdot ]$
by picking the policy minimizing the
expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:
\begin{align}
\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t. }p\text{ evaluates to }S} \text{cost}(p) \nonumber
\end{align}
%Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g. DeepCoder~\citep{BalGauBroetal16}.

@@

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level image editing.
For example,
we could change all of the circles to squares or make all of the lines be dashed,
or we can (automatically) extrapolate figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and is a practical application:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
\begin{figure}[H]\centering
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: drawings. Bottom, black: extrapolations automatically produced by our system.}
  \label{extrapolationFigure}\vspace{-0.25cm}
  \end{figure}
%\input{extrapolations.tex}

@@

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images using a combination of learning, stochastic search, and program synthesis.
%We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an AI write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
\#1753684, and the MUSE program (DARPA grant FA8750-14-2-0242).

>>>>

\begin{table}[t]
  \caption{Drawings (left), their specs (middle left), and programs synthesized from those specs (middle right). Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands. Note the nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
%  \vspace{-0.6cm}
\centering  \begin{tabular}{m{1.5cm}llc}
    \toprule
    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
      \textbf{Compression factor}%\\\textbf{factor}
      %      \end{tabular}\\
      \\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{lstlisting}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
for(i<3)
 line(i,-1*i+6,
      2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{lstlisting}
     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(5,13,2,10,arrow)
%% Circle(5,9)
%% Circle(8,5)
%% Line(2,8, 2,6,arrow)
%% Circle(2,5)
%% \end{lstlisting}
%% \small\emph{... etc. ...; 13 lines}
%% \end{minipage}&
%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
%% circle(4,10)
%% for(i<3)
%%  circle(-3*i+7,5)
%%  circle(-3*i+7,1)
%%  line(-3*i+7,4,-3*i+7,2,arrow)
%%  line(4,9,-3*i+7,6,arrow)
%% \end{lstlisting}
%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Circle(5,8)
Circle(2,8)
Circle(8,11)
Line(2,9, 2,10)
Circle(8,8)
Line(3,8, 4,8)
Line(3,11, 4,11)
\end{lstlisting}
  \small\emph{... etc. ...; 21 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<3)
 for(j<3)
  if(j>0)
   line(-3*j+8,-3*i+7,
        -3*j+9,-3*i+7)
   line(-3*i+7,-3*j+8,
        -3*i+7,-3*j+9)
  circle(-3*j+7,-3*i+7)
\end{lstlisting}
\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Rectangle(1,10,3,11)
Rectangle(1,12,3,13)
Rectangle(4,8,6,9)
Rectangle(4,10,6,11)
\end{lstlisting}
  \small\emph{... etc. ...; 16 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<4)
 for(j<4)
  rectangle(-3*i+9,-2*j+6,
            -3*i+11,-2*j+7)
\end{lstlisting}
\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(11,14,13,14,arrow)
Circle(10,10)
Line(10,13,10,11,arrow)
Circle(6,10)
\end{lstlisting}
    \small\emph{... etc. ...; 15 lines}
\end{minipage}&
\begin{minipage}{\exampleProgramSize}
    \begin{lstlisting}
for(i<4)
 line(-4*i+13,4,-4*i+13,2,arrow)
 for(j<3)
  if(j>0)
   circle(-4*i+13,4*j+-3)
  line(-4*j+10,5,-4*j+12,5,
       arrow)
\end{lstlisting}
  \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule    
  \includegraphics[width = \exampleDrawingSize]{figures/expert-71-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(3,10,3,14,arrow)
Rectangle(11,8,15,10)
Rectangle(11,14,15,15)
Line(13,10,13,14,arrow)
  \end{lstlisting}\small\emph{... etc. ...; 16 lines}
  \end{minipage}&\begin{minipage}{\exampleProgramSize}
%% \begin{lstlisting}
%% for (i<3)
%%  circle(-3*i+7,1)
%%  circle(-3*i+7,6)
%%  line(-3*i+7,-1*i+4,-3*i+7,5)
%% \end{lstlisting}
\begin{lstlisting}
for(i<3)
 line(7,1,5*i+2,3,arrow)
 for(j<i+1)
  if(j>0)
   line(5*j-1,9,5*i,5,arrow)
  line(5*j+2,5,5*j+2,9,arrow)
 rectangle(5*i,3,5*i+4,5)
 rectangle(5*i,9,5*i+4,10)
rectangle(2,0,12,1)
\end{lstlisting}
\end{minipage}&$\frac{16}{9} = 1.8\text{x}$\\\midrule

@@

\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Circle(2,8)
Rectangle(6,9, 7,10)
Circle(8,8)
Rectangle(6,12, 7,13)
Rectangle(3,9, 4,10)
\end{lstlisting}\small\emph{... etc. ...; 9 lines}
  \end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
reflect(y=8)
 for(i<3)
  if(i>0)
   rectangle(3*i-1,2,3*i,3)
  circle(3*i+1,3*i+1)
\end{lstlisting}
\end{minipage}&$\frac{9}{5} = 1.8\text{x}$ \\\bottomrule
  \end{tabular}\vspace{-0.5cm}
  \end{table}

@@

Given a search policy, what is the best way of using it to quickly find minimum cost programs?
We use a bias-optimal search algorithm (c.f. Schmidhuber 2004~\citep{schmidhuber2004optimal}):
\\\noindent\textbf{Definition: Bias-optimality.} 
   A search algorithm is $n$-\emph{bias optimal}
with respect to a distribution $\probability_{\text{bias}}[\cdot ]$ if it is
guaranteed to find a solution in $\sigma $ after searching for at least time
$n\times\frac{t(\sigma )}{\probability_{\text{bias}}[\sigma ]}$, where $t(\sigma )$ is the time it
takes to verify that $\sigma $ contains a solution to the
search problem.

%Intuitively, an $n$-bias optimal search algorithm spends at least $\probability_{\text{bias}}[\sigma ]/n$ of its time exploring solution space $\sigma $.
Bias-optimal search over program spaces is known as \textbf{Levin
  Search}~\cite{levin1973universal}; an example of a $1$-bias optimal
search algorithm is an ideal time-sharing system that allocates
$\probability_{\text{bias}}[\sigma ]$ of its time to trying $\sigma $.
We construct a $1$-bias optimal search algorithm by identifying
$\probability_{\text{bias}}[\sigma ] = \pi_\theta(\sigma |S)$ and
$t(\sigma ) = t(\sigma|S)$, where $t(\sigma|S)$ is how long the
synthesizer takes to search $\sigma $ for a program for
$S$. Intuitively, this means that the search algorithm explores the
entire program space, but spends most of its time in the regions of
the space that the policy judges to be most promising.  Concretely,
this means that we run many different
program searches \emph{in parallel} (i.e., run in parallel different
instances of the synthesizer, one for each $\sigma$), but to
allocate compute time to a $\sigma $ in proportion to
$\pi_\theta(\sigma |S)$.

\begin{comment}
\begin{figure}\centering
  \begin{minipage}[c]{0.45\textwidth}
    \begin{tikzpicture}[scale=0.8]
        \node[anchor = west] at (1,4.25) {Entire program search space};
        \footnotesize
    \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (7,4);
    \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(7,0)--(0,0);
    \draw [fill = yellow, opacity = 0.4] (0,4)--(0,1)--(6,4);
    \draw [fill = yellow, opacity = 0.6] (4.5,4)--(5.2,0)--(7,0)--(7,4);
    \draw (0,2) -- node[below,sloped]{short programs} (7,0);
    \draw (0,2) -- node[above,sloped]{long programs} (7,0);
    \draw[align=center] (4.5,4) -- node[above,sloped]{programs w/ \\reflections} (5.2,0);
    \draw[align=center] (0,1) -- node[above,sloped]{ programs w/ \\loops} (6,4);
    %% \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}|S) = $};
    %% \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
    %%    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}|S) = $};

    \node(p2)[anchor =west ] at (0,-0.5) {$\pi_\theta(\text{long, loops}|S) = $};
    \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
    \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}|S) = $};
    \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);

    %% \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}|S) = $};
    %% \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);

    \node(p5)[anchor =west ] at ([yshift = 8pt,xshift=20pt]p3.east) {\emph{etc.}};
  \end{tikzpicture}
    \end{minipage}
  \begin{minipage}[c]{0.5\textwidth}
          \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs. For example, one subspace might be short programs which don't loop. The policy $\pi$ predicts a distribution over program subspaces. The weight that $\pi$ assigns to a subspace is indicated by its yellow shading in the figure to the left, and is conditioned on the spec $S$.}
    \end{minipage}\vspace{-0.5cm}
\end{figure}
  \end{comment}

Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
But the actual runtime of the algorithm depends strongly upon
the bias $\probability_{\text{bias}}[\cdot ]$.
Our new approach is to learn $\probability_{\text{bias}}[\cdot ]$
by picking the policy minimizing the
expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:
\begin{align}
\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t. }p\text{ evaluates to }S} \text{cost}(p) \nonumber
\end{align}
%Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g. DeepCoder~\citep{BalGauBroetal16}.

@@

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level image editing.
For example,
we could change all of the circles to squares or make all of the lines be dashed,
or we can (automatically) extrapolate figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and is a practical application:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
\begin{figure}[H]\centering
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: drawings. Bottom, black: extrapolations automatically produced by our system.}
  \label{extrapolationFigure}%\vspace{-0.8cm}
  \end{figure}
%\input{extrapolations.tex}

@@

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images using a combination of learning, stochastic search, and program synthesis.
%We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an AI write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture, and for funding from NSF GRFP, NSF Award 
\#1753684, the MUSE program (DARPA grant FA8750-14-2-0242),
and AFOSR award FA9550-16-1-0012.
This material is based upon work supported by the Center for Brains, Minds and Machines (CBMM), funded by NSF STC award CCF-1231216.

\subsubsection*{Code, data, and drafts}
A longer version of this paper is available at~\url{https://arxiv.org/abs/1707.09627}.
The code and data are available at~\url{https://github.com/ellisk42/TikZ}.
